\subsection{Default Arguments}

One common use case of using aliases was to define commands with default arguments.
More specifically, we refer to an alias as defining default arguments when the alias name is the same as the command name, and the command specifies at least one further argument.
This phenomenon can be already observed in Tables \ref{tab:top-summary} and \ref{tab:command-summary} for commands \verb|ls| and \verb|grep| (e.g., \verb|alias ls=ls -G| or \verb|alias grep=grep -i|).
Overall, aliases defining default arguments make up a sizable amount of 502801 (10.5\%) of all alias definitions. 
Interestingly, a majority of these aliases, 278370 (55.4\%), deal with enabling color in commands (e.g., \verb|--color=auto|, \verb|--color=always|).
The top 3 of aliases (or 6 depending on whether you'd want to count basic synonyms separately) make up more than 95\% of the 55.4\%: \verb|{dir, vdir}| (21.7\%), \verb|ls| (26.5\%), and \verb|{grep, fgrep, egrep}| (49.3\%).
Since aliases defining color as their default argument would disproportionally skew any relative measure from other data we observed, we will exclude them when reporting summary statistics for the remainder of this section.

To a much lesser extent, we saw two other patterns emerging: (1) enabling safety and interactivity, and (2) enabling human-readable and verbose outputs.
We also saw safety and interactivity as part of a broader trend beyond just aliases for default arguments and report more results on this pattern in Section \ref{sec:safety}.
To quickly summarize the extent within default arguments: 64497 aliases define safety and interactivity arguments (or 28.7\% of overall default argument aliases without color options).
Default arguments that enable human-readable and verbose outputs were present in 35080 aliases (or 15.6\% of overall default argument aliases without color options).
Table \ref{tab:default-arguments-overview} provides an overview of the most common aliases defining default arguments (when removing color options).
\TODO add actual table here

